# Challenge 07: Auto ML 1

## Code to visualize attrition data

Loading the libraries and data

```{r}
# Libraries 
library(tidyverse)
library(readxl)
library(skimr)
library(GGally)

# Load Data data definitions

path_data_definitions <- "07_Data/data_definitions.xlsx"
definitions_raw_tbl   <- read_excel(path_data_definitions, sheet = 1, col_names = FALSE)

# Load Data

employee_attrition_tbl <- read_csv("07_data\\datasets-1067-1925-WA_Fn-UseC_-HR-Employee-Attrition.txt")
employee_attrition_tbl
```


Function to plot different features

```{r}
# Create data tibble, to potentially debug the plot_ggpairs function (because it has a data argument)

plot_ggpairs <- function(data, color = NULL, density_alpha = 0.5) {
    
    color_expr <- enquo(color)
    
    if (rlang::quo_is_null(color_expr)) {
        
        g <- data %>%
            ggpairs(lower = "blank") 
        
    } else {
        
        color_name <- quo_name(color_expr)
        
        g <- data %>%
            ggpairs(mapping = aes_string(color = color_name), 
                    lower = "blank", legend = 1,
                    diag = list(continuous = wrap("densityDiag", 
                                                  alpha = density_alpha))) +
            theme(legend.position = "bottom")
    }
    
    return(g)
    
}
```


Explore Features by Category

```{r}
#   1. Descriptive features: age, gender, marital status 
employee_attrition_tbl %>%
    select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome) %>%
    plot_ggpairs(Attrition)

#   2. Employment features: department, job role, job level
employee_attrition_tbl %>%
    select(Attrition, contains("employee"), contains("department"), contains("job")) %>%
    plot_ggpairs(Attrition) 

#   3. Compensation features: HourlyRate, MonthlyIncome, StockOptionLevel 
employee_attrition_tbl %>%
    select(Attrition, contains("income"), contains("rate"), contains("salary"), contains("stock")) %>%
    plot_ggpairs(Attrition)

#   4. Survey Results: Satisfaction level, WorkLifeBalance 
employee_attrition_tbl %>%
    select(Attrition, contains("satisfaction"), contains("life")) %>%
    plot_ggpairs(Attrition)

#   5. Performance Data: Job Involvment, Performance Rating
employee_attrition_tbl %>%
    select(Attrition, contains("performance"), contains("involvement")) %>%
    plot_ggpairs(Attrition)

#   6. Work-Life Features 
employee_attrition_tbl %>%
    select(Attrition, contains("overtime"), contains("travel")) %>%
    plot_ggpairs(Attrition)

#   7. Training and Education 
employee_attrition_tbl %>%
    select(Attrition, contains("training"), contains("education")) %>%
    plot_ggpairs(Attrition)

#   8. Time-Based Features: Years at company, years in current role
employee_attrition_tbl %>%
    select(Attrition, contains("years")) %>%
    plot_ggpairs(Attrition)
```





## CHALLENGE QUESTIONS


#### 1. Compensation Features

What can you deduce about the interaction between Monthly Income and Attrition?

1. Those that are leaving the company have a higher Monthly Income
2. That those are staying have a lower Monthly Income
3. **Those that are leaving have a lower Monthly Income**
4. It's difficult to deduce anything based on the visualization


#### 2. Compensation Features

What can you deduce about the interaction between Percent Salary Hike and Attrition?

1.Those that are leaving the company have a higher Percent Salary Hike
2.Those that are staying have a lower Percent Salary Hike
3. Those that are leaving have lower Percent Salary Hike
4. **It's difficult to deduce anything based on the visualization**


#### 3. Compensation Features

What can you deduce about the interaction between Stock Option Level and Attrition?

1. Those that are leaving the company have a higher stock option level
2. **Those that are staying have a higher stock option level**
3. It's difficult to deduce anything based on the visualization


#### 4. Survey Results

What can you deduce about the interaction between Environment Satisfaction and Attrition?

1. **A higher proportion of those leaving have a low environment satisfaction level**
2. A higher proportion of those leaving have a high environment satisfaction level
3. It's difficult to deduce anything based on the visualization


#### 5. Survey Results

What can you deduce about the interaction between Work Life Balance and Attrition

1. Those that are leaving have higher density of 2's and 3's
2. **Those that are staying have a higher density of 2's and 3's**
3. Those that are staying have a lower density of 2's and 3's
4. It's difficult to deduce anything based on the visualization


#### 6. Performance Data

What Can you deduce about the interaction between Job Involvement and Attrition?

1. **Those that are leaving have a lower density of 3's and 4's**
2. Those that are leaving have a lower density of 1's and 2's
3. Those that are staying have a lower density of 2's and 3's
4. It's difficult to deduce anything based on the visualization


#### 7. Work-Life Features

What can you deduce about the interaction between Over Time and Attrition?

1. The proportion of those leaving that are working Over Time are high compared to those that are not leaving
2. **The proportion of those staying that are working Over Time are high compared to those that are not staying**


#### 8. Training and Education

What can you deduce about the interaction between Training Times Last Year and Attrition

1. People that leave tend to have more annual trainings
2. People that leave tend to have less annual trainings
3. **It's difficult to deduce anything based on the visualization**


#### 9. Time-Based Features

What can you deduce about the interaction between Years At Company and Attrition

1. People that leave tend to have more working years at the company
2. **People that leave tend to have less working years at the company**
3. It's difficult to deduce anything based on the visualization


#### 10. Time-Based Features

What can you deduce about the interaction between Years Since Last Promotion and Attrition?

1. Those that are leaving have more years since last promotion than those that are staying
2. Those that are leaving have fewer years since last promotion than those that are staying
3. **It's difficult to deduce anything based on the visualization**


